---
output:
  md_document:
    variant: markdown_github
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```
# avocado

The dataset contains historical data on avocado prices and sales volume in multiple US markets. [source data](https://www.kaggle.com/neuromusic/avocado-prices/home) is from [kaggle](https://www.kaggle.com/).

For more relevant data, please refer to [here](http://www.hassavocadoboard.com/retail/volume-and-price-data)


## Installation

You can install the avocado package from [my github](https://github.com/Irissq28/avocado) or run the code below in console.

```{r}
devtools::install_github("Irissq28/avocado")
```

## Example

Load the package.

```{r}
library(avocado)
```

Familiar with the data frame.

```{r}
summary(avocado)
```

```{r}
df_head <- head(avocado)
knitr::kable(df_head, align = "c")
```

Load `ggplot`, `tidyverse` and `dplyr` to make a simple plot, which shows the total number of each type of avocados sold each year.

```{r}
library(ggplot2)
library(tidyverse)
library(dplyr)
avocado %>%
  group_by(type)  %>%
  ggplot(aes(x = year,y = `Total Volume`, color = type)) +
  theme_bw() +
  geom_point() +
  theme(plot.title = element_text(size = 13, hjust = 0.5)) +
  labs(x="year",y="Total Volume",
       title="Total number of each type of avocados sold each year")
```

The table shows the mean number of avocados sold of each region.

```{r}
sold_average <-avocado %>%
  filter(year == 2018) %>%
  group_by(region) %>%
  summarise(`Total Volume Mean` = mean(`Total Volume`))

knitr::kable(head(sold_average), align = "c")
```

The plot shows the region where the mean of total number of avocados sold larger than the mean of each region.

```{r}
sold_average %>%
  filter(`Total Volume Mean` > mean(`Total Volume Mean`)) %>%
  ggplot(aes(x= `Total Volume Mean`, y = region)) +
  geom_point() +
  theme_bw() +
  theme(plot.title = element_text(size = 9, hjust = 0.5)) +
  labs(x="Mean of Total Volume",y="region",
       title="The region where the mean of total number of avocados sold larger than the mean of each region")
```


